---
title: "ISLR CHAPTER 2"
author: "Nikam Vikrant Dipak"
date: "`r Sys.Date()`"
output:
  word_document: default
  html_document: default
---

#Q.8 This exercise relates to the College data set, which can be found in the fle College.csv on the book website. It contains a number of variables for 777 diferent universities and colleges in the US. The variables are
#(a) Use the read.csv() function to read the data into R. Call the loaded data college. Make sure that you have the directory set to the correct location for the data.
```{r}
#if ISLR2 library is not installed then you can install it first by using install.packages("ISLR2")
library(ISLR2)
college=read.csv("C:\\Users\\vikra\\Downloads\\ISLR R\\College.csv",header = T)
names(college) #to get the variable names
#Your data file should be in the same directory as you are working
```
#(b) Look at the data using the View() function. You should notice that the frst column is just the name of each university. We don’t really want R to treat this as data. However, it may be handy to have these names for later. Try the following commands:

```{r}
View(college)
rownames(college)=college[,1]  #Will treat given respected columns as rownames or row heading
View(college)
college=college[,-1]
View(college)
college
```
#(c) i. Use the summary() function to produce a numerical summary of the variables in the data set.
```{r}
summary(college)
```
#(c)ii. Use the pairs() function to produce a scatterplot matrix of the frst ten columns or variables of the data. Recall that you can reference the frst ten columns of a matrix A using A[,1:10]
```{r}
pairs(college[,2:17])
```

#(c) iii. Use the plot() function to produce side-by-side boxplots of Outstate versus Private.
```{r}
Outstate=as.factor(college$Outstate)
Private=as.factor(college$Private)
boxplot(college$Outstate~college$Private)
plot(Outstate~factor(Private),data = college)
```
#(c) iv. Create a new qualitative variable, called Elite, by binning the Top10perc variable. We are going to divide universities into two groups based on whether or not the proportion of students coming from the top 10 % of their high school classes exceeds 50 %
#Use the summary() function to see how many elite universities there are. Now use the plot() function to produce side-by-side boxplots of Outstate versus Elite.
```{r}
Elite=rep("No",nrow(college))
Elite[college$Top10perc>50]="Yes"
Elite=as.factor(Elite)
college=data.frame(college,Elite)
View(college)
summary(college$Elite)
plot(college$Elite,college$Outstate)
```

#(c) v. Use the hist() function to produce some histograms with difering numbers of bins for a few of the quantitative variables. You may fnd the command par(mfrow = c(2, 2)) useful: it will divide the print window into four regions so that four plots can be made simultaneously. Modifying the arguments to this function will divide the screen in other ways
```{r}
par(mfrow=c(2,2))
for(i in seq(15,30,5)){
  hist(college$Enroll,breaks=i)
}



```
#This exercise involves the Auto data set studied in the lab. Make sure that the missing values have been removed from the data.
```{r}
auto=read.table('Auto.data',header=T)
dim(auto)
auto=na.omit(auto) #remove missing values
dim(auto)
```
#(a) Which of the predictors are quantitative, and which are qualitative?
```{r}
str(auto)
```
#(b)What is the range of each quantitative predictor? You can answer this using the range() functionsapply(auto,range)
```{r}
sapply(auto,range)
```
#(c) What is the mean and standard deviation of each quantitative predictor?
```{r}
summary(auto)
round(sapply(auto,mean),2)
#Pulling together qualitative predictors
quantitative_columns=auto[,-c(4,9)]
sapply(quantitative_columns,mean)
sapply(quantitative_columns,sd)
summary(quantitative_columns)

```
#(d) Now remove the 10th through 85th observations. What is the range, mean, and standard deviation of each predictor in the subset of the data that remains?
```{r}
auto=auto[-c(seq(10,85)),]
auto
reduced_quantitative_columns=auto[,-c(4,9)]
summary(reduced_quantitative_columns)
```
#(e) Using the full data set, investigate the predictors graphically, using scatterplots or other tools of your choice. Create some plots highlighting the relationships among the predictors. Comment on your fndings.
```{r}
pairs(auto[,c(1,2,3,5,6,7,8)])  
cor(auto[,c(1,2,3,5,6,7,8)])  
```


#10. This exercise involves the Boston housing data set.
```{r}
library(ISLR2)
Boston
dim(Boston)
pairs(Boston)
plot(Boston)
cor(Boston)
sum(Boston$chas==1)
table(Boston$chas)
median(Boston$ptratio)
sum(Boston$rm>7)
sum(Boston$rm>8)
par(mfrow=c(1,3))
boxplot(Boston$crim, xlab = "crim")
boxplot(Boston$tax, xlab = "tax")
boxplot(Boston$ptratio, xlab = "ptratio")
which(Boston$medv == min(Boston$medv))
summary(Boston)
summary(subset(Boston, rm > 8))
range(Boston$lstat)
range(Boston$ptratio)
```

